Optimizing Structural Properties Of Neural Networks With Genetic Algorithms

### 2015-08-02 paper/paper.tex
genetic algorithm mk 1

>>>>

In each iteration of the algorithm, a generation (set) of $N$ individuals (Generators) $G_t = \left\{ g_i \right\}$ is converted into
a new one $G_{t+1}$ according to the following scheme:
\begin{description}
 \item[Evaluation] The fitness $f_i = F_C(g_i)$ of each individual is mesasured using at least 20 samples (and adaptively more if the $f_i$ are spaced closely, to at msot 100).
 \item[Selection] All individuals are grouped into disjunct pairs for which we check which one has the higher $f$. This is repeated $K=10$ times, counting the wins of each individual. Based thereon we use the $p=50\%$ best individuals $S$ to build the next generation.

By using pair comparisons instead of simple ordering according to $f$, we allow weaker individuals to continue into the next generation albeit with low probability), keeping the gene pool more diverse.

\item[Reproduction]
We generate the next generation $G_{t+1}$ by first generating $2N$ candidates by \emph{mutating} or \emph{recombining} elements of $S$, i.e. either changing a single parameter randomly or taking two individuals and randomly choose for each parameter from which parent to take the value. 
We then perform a single sample fitness test and remove all networks that fail, until only $N$ networks are left which form $G_{t+1}$. 
This way, the most unpromising elements of the new generation are removed before the expensive fitness evaluation. 
\end{description}
